`r params$doc_title`

### 2022-12-16 scripts/MSc.Rmd
issue standard deviation for simulating from normal distribution detected

- Issues from discussion mentioned above

@@

```{r PVE_BMI_vs_pval, warning=FALSE}
# labeling (only FTO label)
my_data_harm$gene_label <- NA
my_data_harm$gene_label[my_data_harm$SNP %in% filter_FTO$refsnp_id] <- "FTO"

# color labeling
my_data_harm$fto_col_annot <- "No FTO variant"
my_data_harm$fto_col_annot[my_data_harm$SNP %in% filter_FTO$refsnp_id] <- "FTO variant"

>>>>

- Issues from discussion mentioned above
- Interchanged panel A and panel B in the first version of Figure 1, used the same colours in panel B and in the legends
- Added five estimates for "BMI -> GSD": Wald estimate (FTO), Wald estimate (MC4R variant), random IVW, MRMix, weighted mode

@@

```{r PVE_BMI_vs_pval, warning=FALSE}
# labeling (only FTO label)
my_data_harm$gene_label <- NA
my_data_harm$gene_label[my_data_harm$SNP %in% filter_FTO$refsnp_id] <- "FTO/MC4R"

# color labeling
my_data_harm$fto_col_annot <- "No FTO/MC4R variant"
my_data_harm$fto_col_annot[my_data_harm$SNP %in% filter_FTO$refsnp_id] <- "FTO/MC4R variant"
